### 2015-05-29 article/graphs/ftp-bench-comparison.tex
article

%%%%%%%%%%%%%%%%%%%%%%%%
% CPU in the background
%%%%%%%%%%%%%%%%%%%%%%%%
\begin{axis}[
        width  = 0.4*\textwidth,
        height = 5cm,
        major x tick style = transparent,
        ybar=2pt,%space between the bars
        bar width=10pt,
        enlarge x limits={abs=1},
        ylabel = {CPU\#0 usage},
        hide x axis,
        axis y line*=right,
        ymin=0, ymax=100,
        symbolic x coords={oot, openSSH, OpenVPN, IPSec},
        xtick = data,
        scaled y ticks = false,%Disable the *10^4 exponent applied to all y axis markings.
        legend style={at={(0.5,-0.45)}, anchor=north,legend columns=4},
        enlarge x limits=0.1,
    ]

\addplot[style={black,fill=LimeGreen,postaction={pattern=north east lines},mark=none}]
    coordinates {
        (oot, 0)
        (openSSH, 89.29)
        (OpenVPN, 76.03)
        (IPSec, 74.64)
    };
    \label{software}

\addplot[style={black,fill=RedOrange,postaction={pattern=north east lines},mark=none}]
    coordinates {
        (oot, 0)
        (openSSH, 68.29)
        (OpenVPN, 80.89)
        (IPSec, 17.25)
    };
    \label{hardware}

\addplot[style={black,fill=gray,postaction={pattern=north east lines},mark=none}]
    coordinates {
        (oot, 7.16)
        (openSSH, 0)
        (OpenVPN, 0)
        (IPSec, 0)
    };
    \label{oot}%"oot" for "out of tunnel"
\legend{software, hardware, oot}
\end{axis}

%%%%%%%%%%%%%%%%%%%%%%%%
% throughput
%%%%%%%%%%%%%%%%%%%%%%%%
\begin{axis}[
        % title = {Comparison over file transfer methods},
        width  = 0.4*\textwidth,
        height = 5cm,
        major x tick style = transparent,
        ybar=6pt,
        bar width=6pt,
        enlarge x limits={abs=1},
        ymajorgrids = true,
        ylabel = {Throughtput [MB/s]},
        xlabel = {},
        ymin=0, ymax=12,
        symbolic x coords={oot, openSSH, OpenVPN, IPSec},
        xtick = data,
        x tick label style={rotate=45,anchor=east},
        scaled y ticks = false,%Disable the *10^4 exponent applied to all y axis markings.
        % legend style={at={(0.5,-0.25)}, anchor=north,legend columns=2},
        enlarge x limits=0.1,
    ]

\addplot[style={black,fill=ForestGreen,mark=none}]
    coordinates {
        (oot, 0)
        (openSSH, 8.19)
        (OpenVPN, 3.87)
        (IPSec, 6.47)
    };
    \label{soft-tp}

\addplot[style={black,fill=BrickRed,mark=none}]
    coordinates {
        (oot, 0)
        (openSSH, 10.39)
        (OpenVPN, 2.84)
        (IPSec, 5.80)
    };
    \label{hardware-tp}

\addplot[style={black,fill=black,mark=none}]
    coordinates {
        (oot, 11.39)
        (openSSH, 0)
        (OpenVPN, 0)
        (IPSec, 0)
    };
    \label{oot-tp}%"tp" for "throughput"
\legend{}
\end{axis}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%
% CPU in the background
%%%%%%%%%%%%%%%%%%%%%%%%
\begin{axis}[
        width  = 0.4*\textwidth,
        height = 5cm,
        major x tick style = transparent,
        ybar=2pt,%space between the bars
        bar width=10pt,
        enlarge x limits={abs=1},
        ylabel = {CPU\#0 usage},
        hide x axis,
        axis y line*=right,
        ymin=0, ymax=100,
        symbolic x coords={Normal, openSSH, OpenVPN, IPSec},
        xtick = data,
        scaled y ticks = false,%Disable the *10^4 exponent applied to all y axis markings.
        legend style={at={(0.5,-0.45)}, anchor=north,legend columns=4},
        enlarge x limits=0.1,
    ]

\addplot[style={black,fill=LimeGreen,postaction={pattern=north east lines},mark=none}]
    coordinates {
        (Normal, 0)
        (openSSH, 89.29)
        (OpenVPN, 76.03)
        (IPSec, 74.64)
    };
    \label{software-cpu}

\addplot[style={black,fill=RedOrange,postaction={pattern=north east lines},mark=none}]
    coordinates {
        (Normal, 0)
        (openSSH, 68.29)
        (OpenVPN, 80.89)
        (IPSec, 17.25)
    };
    \label{hardware-cpu}

\addplot[style={black,fill=gray,postaction={pattern=north east lines},mark=none}]
    coordinates {
        (Normal, 7.16)
        (openSSH, 0)
        (OpenVPN, 0)
        (IPSec, 0)
    };
    \label{Normal-cpu}%"Normal" for "out of tunnel"
\end{axis}

%%%%%%%%%%%%%%%%%%%%%%%%
% throughput
%%%%%%%%%%%%%%%%%%%%%%%%
\begin{axis}[
        % title = {Comparison over file transfer methods},
        width  = 0.4*\textwidth,
        height = 5cm,
        major x tick style = transparent,
        ybar=6pt,
        bar width=6pt,
        enlarge x limits={abs=1},
        ymajorgrids = true,
        ylabel = {Throughtput [MB/s]},
        xlabel = {},
        ymin=0, ymax=12,
        symbolic x coords={Normal, openSSH, OpenVPN, IPSec},
        xtick = data,
        x tick label style={rotate=45,anchor=east},
        scaled y ticks = false,%Disable the *10^4 exponent applied to all y axis markings.
        % legend style={at={(0.5,-0.25)}, anchor=north,legend columns=2},
        legend style={at={(0.5,-0.45)}, anchor=north,legend columns=3},
        enlarge x limits=0.1,
        nodes near coords,
        enlarge y limits={value=0.4,upper},
        every node near coord/.append style={rotate=90, anchor=west},%This needs to be after 'ybar'
    ]

\addplot[style={black,fill=ForestGreen,mark=none}]
    coordinates {
        (Normal, 0)
        (openSSH, 8.19)
        (OpenVPN, 3.87)
        (IPSec, 6.47)
    };
    \label{software}

\addplot[style={black,fill=BrickRed,mark=none}]
    coordinates {
        (Normal, 0)
        (openSSH, 10.39)
        (OpenVPN, 2.84)
        (IPSec, 5.80)
    };
    \label{hardware}

\addplot[style={black,fill=black,mark=none}]
    coordinates {
        (Normal, 11.39)
        (openSSH, 0)
        (OpenVPN, 0)
        (IPSec, 0)
    };
    \label{Normal}%"tp" for "throughput"
\legend{software, hardware, Normal}
\end{axis}

### 2015-05-29 article/graphs/openvpn-tls-bench.tex
article

%%%%%%%%%%%%%%%%%%%%%%%%
% CPU in the background
%%%%%%%%%%%%%%%%%%%%%%%%
\begin{axis}[
        width  = 0.4*\textwidth,
        height = 5cm,
        major x tick style = transparent,
        ybar=2pt,%space between the bars
        bar width=10pt,
        enlarge x limits={abs=1},
        ylabel = {CPU\#0 usage},
        hide x axis,
        axis y line*=right,
        ymin=0, ymax=100,
        symbolic x coords={RSA-1024, RSA-2048, RSA-4096},
        xtick = data,
        scaled y ticks = false,%Disable the *10^4 exponent applied to all y axis markings.
        legend style={at={(0.5,-0.20)}, anchor=north,legend columns=2},
        enlarge x limits=0.4,
    ]

\addplot[style={black,fill=LimeGreen,postaction={pattern=north east lines},mark=none}]
    coordinates {
        (RSA-1024, 40.32)
        (RSA-2048, 92.14)
        (RSA-4096, 81.97)
    };
    \label{software}

\addplot[style={black,fill=RedOrange,postaction={pattern=north east lines},mark=none}]
    coordinates {
        (RSA-1024, 13.29)
        (RSA-2048, 4.82)
        (RSA-4096, 4.78)
    };
    \label{hardware}
\legend{software, hardware}
\end{axis}

%%%%%%%%%%%%%%%%%%%%%%%%
% throughput
%%%%%%%%%%%%%%%%%%%%%%%%
\begin{axis}[
        title = {TLS connections through OpenVPN},
        width  = 0.4*\textwidth,
        height = 5cm,
        major x tick style = transparent,
        ybar=6pt,
        bar width=6pt,
        enlarge x limits={abs=1},
        ymajorgrids = true,
        ylabel = {Throughtput [MB/s]},
        xlabel = {},
        ymin=0,
        symbolic x coords={RSA-1024, RSA-2048, RSA-4096},
        xtick = data,
        scaled y ticks = false,%Disable the *10^4 exponent applied to all y axis markings.
        % legend style={at={(0.5,-0.25)}, anchor=north,legend columns=2},
        enlarge x limits=0.4,
    ]

\addplot[style={black,fill=ForestGreen,mark=none}]
    coordinates {
        (RSA-1024, 445.4)
        (RSA-2048, 155.6)
        (RSA-4096, 19.6)
    };
    \label{soft-tp}

\addplot[style={black,fill=BrickRed,mark=none}]
    coordinates {
        (RSA-1024, 509.3)
        (RSA-2048, 420.9)
        (RSA-4096, 115.5)
    };
    \label{hardware-tp}
\legend{}
\end{axis}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%
% CPU in the background
%%%%%%%%%%%%%%%%%%%%%%%%
\begin{axis}[
        width  = 0.4*\textwidth,
        height = 5cm,
        major x tick style = transparent,
        ybar=2pt,%space between the bars
        bar width=10pt,
        enlarge x limits={abs=1},
        ylabel = {CPU\#0 usage},
        hide x axis,
        axis y line*=right,
        ymin=0, ymax=100,
        symbolic x coords={Low, Medium, High},
        xtick = data,
        scaled y ticks = false,%Disable the *10^4 exponent applied to all y axis markings.
        legend style={at={(0.5,-0.20)}, anchor=north,legend columns=2},
        enlarge x limits=0.4,
    ]

\addplot[style={black,fill=LimeGreen,postaction={pattern=north east lines},mark=none}]
    coordinates {
        (Low, 40.32)
        (Medium, 92.14)
        (High, 81.97)
    };
    \label{software-cpu}

\addplot[style={black,fill=RedOrange,postaction={pattern=north east lines},mark=none}]
    coordinates {
        (Low, 13.29)
        (Medium, 4.82)
        (High, 4.78)
    };
    \label{hardware-cpu}
\end{axis}

%%%%%%%%%%%%%%%%%%%%%%%%
% throughput
%%%%%%%%%%%%%%%%%%%%%%%%
\begin{axis}[
        title = {TLS connections through OpenVPN},
        width  = 0.4*\textwidth,
        height = 5cm,
        major x tick style = transparent,
        ybar=6pt,
        bar width=6pt,
        enlarge x limits={abs=1},
        ymajorgrids = true,
        ylabel = {Connections per minute},
        xlabel = {},
        ymin=0,
        symbolic x coords={Low, Medium, High},
        xtick = data,
        scaled y ticks = false,%Disable the *10^4 exponent applied to all y axis markings.
        % legend style={at={(0.5,-0.25)}, anchor=north,legend columns=2},
        legend style={at={(0.5,-0.20)}, anchor=north,legend columns=2},
        enlarge x limits=0.4,
        nodes near coords,
        enlarge y limits={value=0.45,upper},
        every node near coord/.append style={rotate=90, anchor=west},%This needs to be after 'ybar'
    ]

\addplot[style={black,fill=ForestGreen,mark=none}]
    coordinates {
        (Low, 445.4)
        (Medium, 155.6)
        (High, 19.6)
    };
    \label{software}

\addplot[style={black,fill=BrickRed,mark=none}]
    coordinates {
        (Low, 509.3)
        (Medium, 420.9)
        (High, 115.5)
    };
    \label{hardware}
\legend{software, hardware}
\end{axis}
